---
title: 'Reproducible Research: Peer Assessment 1'
output:
  pdf_document: default
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data

Read in the data 

The dataset table names are:
- Steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
- Date: The date on which the measurement was taken in YYYY-MM-DD format
- Intervals:  Identifier for the 5-minute interval in which measurement was taken

```{r}
dat <-read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

Make an aggregate dataset showing the number of steps taken per day:
```{r,echo = True}
## find the total steps per day 
## aggregate data by date and add up the steps for each day
aggbyDate <- aggregate(steps ~ date, dat, FUN = sum)

```

Make a histogram of the total number of steps taken each day
```{r,echo = True}
## make the histogram
hist(aggbyDate$steps, main = "Total Number of Steps Taken Each Day", xlab = "Steps", ylab = "Frequency")
```

Calculate and report the mean and median of the total number of steps taken per day
```{r,echo = True}
## find mean and Median using the mean and median functions
meanData <- mean(aggbyDate$steps) 
medData <- median(aggbyDate$steps)
```

The mean of this dataset is 10766.19 Steps
The median of this dataset is 10765 Steps

## What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r,echo = True}
##similar to what was done above aggregate the steps by interval and average that for each day
aggbyInterval <- aggregate(steps ~ interval, dat, FUN = mean)

#make the time series plot of the Average Daily Acitivty Pattern
plot(aggbyInterval$interval, aggbyInterval$steps, type = "l", xlab = "5-minute Interval", ylab = "Average Steps", main = "Average Daily Acitvity Pattern")

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
